---
title: "Family Vulnerability and Nutritional Status of Children during COVID-19 Pandemic"
author: "A. Mukramin Yusuf, Dhihram Tenrisau, Healthy Hidayanti,et al."
date: '2021-08-31'
output:
  html_document:
    toc: true
    toc_float: true
---
# Data Processing

## Open package

```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(foreign)
library(nnet)
library(ordinal)
library(MASS)
library(pscl)
library(lmtest)
library(zoo)
library(aod)
library(readxl)
library(tidyverse)
library(ResourceSelection)
library(fastDummies)
library(readr)
```

## Open data

```{r, message=FALSE, warning=FALSE}
setwd("~/backup/document/all manuskrip/lk2pk")
clean_lk2pk <- read_csv("clean_lk2pk.csv")
str(clean_lk2pk)
summary(clean_lk2pk)
dim(clean_lk2pk)
head(clean_lk2pk)
```

## Exploring data

In this section, we will explore the data by using the cross-tabs among several variables
PHK = Layoff/Jobloss
status_kemiskinan = Poverty Status
penghasilan = Income
sumberair = Water Source
pekerjaan_bapak = Father’s Occupation
pekerjaan_ibu = Mother’s Occupation
pendidikan = Parental Education
anc = ANC Visits
tabungan = Family Savings
menyusui = Breastfeeding
usia_balita = Child’s Age


```{r}
table (clean_lk2pk$kurang, clean_lk2pk$PHK)
table (clean_lk2pk$kurang, clean_lk2pk$status_kemiskinan)
table (clean_lk2pk$kurang, clean_lk2pk$gender_balita)
table (clean_lk2pk$kurang, clean_lk2pk$penghasilan)
table (clean_lk2pk$kurang, clean_lk2pk$sumber_air)
table(clean_lk2pk$kurang, clean_lk2pk$pekerjaan_bapak)
table(clean_lk2pk$kurang, clean_lk2pk$pekerjaan_ibu)
table(clean_lk2pk$kurang, clean_lk2pk$pendidikan)
table (clean_lk2pk$kurang, clean_lk2pk$anc)
table (clean_lk2pk$kurang, clean_lk2pk$tabungan)
table (clean_lk2pk$kurang, clean_lk2pk$menyusui)
table(clean_lk2pk$kurang, clean_lk2pk$usia_balita)
```
# Regression Logistic

## Bivariate

```{r}
mylogit1 <- glm(kurang  ~ PHK, data = clean_lk2pk, family = "binomial" )
summary(mylogit1)
confint(mylogit1, level = 0.95)
exp(cbind(OR = coef(mylogit1), confint(mylogit1, level = 0.95)))
mylogit1a <- glm(kurang  ~ non_phk, data = clean_lk2pk, family = "binomial" )
summary(mylogit1a)
exp(cbind(OR = coef(mylogit1a), confint(mylogit1a, level = 0.95)))
mylogit2a <- glm(kurang  ~ kat_jk_perempuan, data = clean_lk2pk, family = "binomial" )
summary(mylogit2a)
exp(cbind(OR = coef(mylogit2a), confint(mylogit2a)))
mylogit3 <- glm(kurang  ~ kat_anc, data = clean_lk2pk, family = "binomial" )
summary(mylogit3)
exp(cbind(OR = coef(mylogit3), confint(mylogit3)))
mylogit4 <- glm(kurang  ~ kat_tabungan, data = clean_lk2pk, family = "binomial" )
summary(mylogit4)
exp(cbind(OR = coef(mylogit4), confint(mylogit4)))
mylogit5 <- glm(kurang  ~ kat_menyusui, data = clean_lk2pk, family = "binomial" )
summary(mylogit5)
exp(cbind(OR = coef(mylogit5), confint(mylogit5)))
mylogit6 <- glm(kurang  ~ kat_penghasilan_bulan_bawah, data = clean_lk2pk, family = "binomial" )
summary(mylogit6)
exp(cbind(OR = coef(mylogit6), confint(mylogit6)))
mylogit6a <- glm(kurang  ~ kat_penghasilan_bulan_atas, data = clean_lk2pk, family = "binomial" )
summary(mylogit6a)
exp(cbind(OR = coef(mylogit6a), confint(mylogit6a)))
mylogit7 <- glm(kurang  ~ kat_kemiskinan, data = clean_lk2pk, family = "binomial" )
summary(mylogit7)
exp(cbind(OR = coef(mylogit7), confint(mylogit7)))
mylogit7a <- glm(kurang  ~ kat_non_kemiskinan, data = clean_lk2pk, family = "binomial" )
summary(mylogit7a)
exp(cbind(OR = coef(mylogit7a), confint(mylogit7a)))
mylogit8 <- glm(kurang  ~ kerja_bapak_buruh, data = clean_lk2pk, family = "binomial" )
summary(mylogit8)
exp(cbind(OR = coef(mylogit8), confint(mylogit8)))
mylogit8a <- glm(kurang  ~ kerja_bapak_pemerintah, data = clean_lk2pk, family = "binomial" )
summary(mylogit8a)
exp(cbind(OR = coef(mylogit8a), confint(mylogit8a)))
mylogit8b <- glm(kurang  ~ kerja_bapak_swasta, data = clean_lk2pk, family = "binomial" )
summary(mylogit8b)
exp(cbind(OR = coef(mylogit8b), confint(mylogit8b)))
mylogit8c <- glm(kurang  ~ kerja_bapak_tidak_kerja, data = clean_lk2pk, family = "binomial" )
summary(mylogit8c)
exp(cbind(OR = coef(mylogit8c), confint(mylogit8c)))
mylogit8d <- glm(kurang  ~ kerja_bapak_wiraswasta, data = clean_lk2pk, family = "binomial" )
summary(mylogit8d)
exp(cbind(OR = coef(mylogit8d), confint(mylogit8d)))
mylogit9 <- glm(kurang  ~ kerja_ibu_tidak_kerja , data = clean_lk2pk, family = "binomial" )
summary(mylogit9)
exp(cbind(OR = coef(mylogit9), confint(mylogit9)))
mylogit9b <- glm(kurang  ~ kerja_ibu_swasta , data = clean_lk2pk, family = "binomial" )
summary(mylogit9b)
exp(cbind(OR = coef(mylogit9b), confint(mylogit9b)))
mylogit9c <- glm(kurang  ~ kerja_ibu_pemerintah , data = clean_lk2pk, family = "binomial" )
summary(mylogit9c)
exp(cbind(OR = coef(mylogit9c), confint(mylogit9c)))
mylogit9d <- glm(kurang  ~ kerja_ibu_wiraswasta , data = clean_lk2pk, family = "binomial" )
summary(mylogit9d)
exp(cbind(OR = coef(mylogit9d), confint(mylogit9d)))
mylogit10 <- glm(kurang  ~ pendidikan_SD , data = clean_lk2pk, family = "binomial" )
summary(mylogit10)
exp(cbind(OR = coef(mylogit10), confint(mylogit10)))
mylogit10b <- glm(kurang  ~ pendidikan_SMP , data = clean_lk2pk, family = "binomial" )
summary(mylogit10b)
exp(cbind(OR = coef(mylogit10b), confint(mylogit10b)))
mylogit10c <- glm(kurang  ~ pendidikan_SMA , data = clean_lk2pk, family = "binomial" )
summary(mylogit10c)
exp(cbind(OR = coef(mylogit10c), confint(mylogit10c)))
mylogit11 <- glm(kurang  ~ kat_anc , data = clean_lk2pk, family = "binomial" )
summary(mylogit11)
exp(cbind(OR = coef(mylogit11), confint(mylogit11)))
mylogit11b <- glm(kurang  ~ kat_non_anc , data = clean_lk2pk, family = "binomial" )
summary(mylogit11b)
exp(cbind(OR = coef(mylogit11b), confint(mylogit11b)))
mylogit12 <- glm(kurang  ~ kat_tabungan , data = clean_lk2pk, family = "binomial" )
summary(mylogit12)
exp(cbind(OR = coef(mylogit12), confint(mylogit12)))
mylogit12b <- glm(kurang  ~ kat_non_tabungan , data = clean_lk2pk, family = "binomial" )
summary(mylogit12b)
exp(cbind(OR = coef(mylogit12b), confint(mylogit12b)))
mylogit13 <- glm(kurang  ~ usia_balita_kurang , data = clean_lk2pk, family = "binomial" )
summary(mylogit13)
exp(cbind(OR = coef(mylogit13), confint(mylogit13)))
mylogit13b <- glm(kurang  ~ usia_balita_lebih , data = clean_lk2pk, family = "binomial" )
summary(mylogit13b)
exp(cbind(OR = coef(mylogit13b), confint(mylogit13b)))
mylogit14 <- glm(kurang  ~  kat_air_kemasan, data = clean_lk2pk, family = "binomial" )
summary(mylogit14)
exp(cbind(OR = coef(mylogit14), confint(mylogit14)))
mylogit14b <- glm(kurang  ~  kat_air_pam, data = clean_lk2pk, family = "binomial" )
summary(mylogit14b)
exp(cbind(OR = coef(mylogit14b), confint(mylogit14b)))
mylogit14c <- glm(kurang  ~  kat_air_sumur, data = clean_lk2pk, family = "binomial" )
summary(mylogit14c)
exp(cbind(OR = coef(mylogit14c), confint(mylogit14c)))
mylogit15 <- glm(kurang  ~  kat_menyusui, data = clean_lk2pk, family = "binomial" )
summary(mylogit15)
exp(cbind(OR = coef(mylogit15), confint(mylogit15)))
mylogit15b <- glm(kurang  ~  kat_non_menyusui, data = clean_lk2pk, family = "binomial" )
summary(mylogit15b)
exp(cbind(OR = coef(mylogit15b), confint(mylogit15b)))
```

## Multivariate

```{r}
mylogit_total1 <- glm( kurang ~ PHK + pendidikan_SD + kat_non_anc, data = clean_lk2pk, family = "binomial")
summary(mylogit_total1)
confint(mylogit_total1)
exp(cbind(OR = coef(mylogit_total1), confint(mylogit_total1)))
mylogit_total1a <- glm( kurang ~ non_phk + pendidikan_SD + kat_non_anc, data = clean_lk2pk, family = "binomial")
summary(mylogit_total1a)
confint(mylogit_total1a)
exp(cbind(OR = coef(mylogit_total1a), confint(mylogit_total1a)))
mylogit_total1b <- glm( kurang ~ non_phk + pendidikan_SMP + kat_non_anc, data = clean_lk2pk, family = "binomial")
summary(mylogit_total1b)
confint(mylogit_total1b)
exp(cbind(OR = coef(mylogit_total1b), confint(mylogit_total1b)))
mylogit_total1c <- glm( kurang ~ non_phk + pendidikan_SMA + kat_non_anc, data = clean_lk2pk, family = "binomial")
summary(mylogit_total1c)
confint(mylogit_total1c)
exp(cbind(OR = coef(mylogit_total1c), confint(mylogit_total1c)))
mylogit_total1d <- glm( kurang ~ PHK + pendidikan_SD + kat_anc, data = clean_lk2pk, family = "binomial")
summary(mylogit_total1d)
confint(mylogit_total1d)
exp(cbind(OR = coef(mylogit_total1d), confint(mylogit_total1d)))
mylogit_total2 <- glm( kurang ~ kat_kemiskinan + kerja_bapak_tidak_kerja + kat_non_anc , data = clean_lk2pk, family = "binomial")
summary(mylogit_total2)
confint(mylogit_total2)
exp(cbind(OR = coef(mylogit_total2), confint(mylogit_total2)))
mylogit_total2b <- glm( kurang ~ kat_non_kemiskinan + kerja_bapak_tidak_kerja + kat_non_anc , data = clean_lk2pk, family = "binomial")
summary(mylogit_total2b)
confint(mylogit_total2b)
exp(cbind(OR = coef(mylogit_total2b), confint(mylogit_total2b)))
mylogit_total2c <- glm( kurang ~ kat_kemiskinan + kerja_bapak_tidak_kerja + kat_anc , data = clean_lk2pk, family = "binomial")
summary(mylogit_total2c)
confint(mylogit_total2c)
exp(cbind(OR = coef(mylogit_total2c), confint(mylogit_total2c)))
mylogit_total2d <- glm( kurang ~ kat_kemiskinan + kerja_bapak_wiraswasta + kat_non_anc , data = clean_lk2pk, family = "binomial")
summary(mylogit_total2d)
confint(mylogit_total2d)
exp(cbind(OR = coef(mylogit_total2d), confint(mylogit_total2d)))
```
# Model fit

We choose the mylogit_total1 and my_logit_total2 as the best model, in this section we test the model
```{r}
pR2(mylogit_total1)
pR2(mylogit_total2)
hl <- hoslem.test(mylogit_total1$y, fitted(mylogit_total1), g=10)
hl$p.value
hl2 <- hoslem.test(mylogit_total2$y, fitted(mylogit_total2), g=10)
hl2$p.value
```
